Solving \\ the \\ 15-Puzzle \\ \& \\ Rubik's Cube

### 2022-09-10 latex/Chapters/Conclusion.tex
update

\Section{Implementation}
I am quite satistified to have had the time to implement and play with so many solvers, from handcrafting my own \textbf{SP} \textit{naive} solver, to implementing \textbf{BFS}, \textbf{DFS}, A$^{*}$, admissible heuristics such as Manhattan for the \textbf{SP} and improving on it via linear constraints penalty, and of course all the machinery necessary to fit, train and exploit some \textbf{DL}, \textbf{DRL} and \textbf{DQL} heuristics to guide search algorithms such as  A$^{*}$ and \textbf{MCTS}. Ideally I would have liked to implement things in C++ for speed and multithreading (especially for \textbf{MCTS}) but time was limited so I decided to prioritize breadth and ease of experimentation over depth and efficiency of implementation. The choice of Python definitely made it much easier to integrate with many of the ecosystem's libraries (matplotlib, pandas and pytorch in particular).

\Section{Deep Reinforcement-Q Learning}
Even though the Deep Reinforcement Learning and Deep Q Learning models were quite capricious at time to train. Choosing the convergence mechanisms and criteria, the interplay of generation of new training data with the inner and outer loop of the \textbf{DRL} and \textbf{DQL} algorithms (see \ref{sec:TheoryDLDRL} and \ref{sec:TheoryDQL}) seemed more of an art than a sicence at times). Obviously a lot more tuning, as well as much longer training time and computing resources would have been necessary to make these techniques more competitive at higher dimensions, but overall I remain extremely impressed by how, all things considered - and given how daunting the project seemed at first, it took me little effort to train successful \textbf{DRL} and \textbf{DQL} models capable of solving puzzles of such large state and action spaces.

\Section{Professional issues}
Bug in Kociemba and software design
See \cite{ManyWorlds}
See \cite{https://doi.org/10.1111/1758-5899.12718} and \cite{Bostrom2014}

>>>>

\Section{Implementation}
I am quite satistified to have had the time to implement and play with so many solvers and methods, spanning so many different \textbf{CS} and \textbf{AI} paradigms, from handcrafting my own \textbf{SP} \textit{naive} solver, playing with Kociemba, to implementing \textbf{BFS}, \textbf{DFS}, A$^{*}$, admissible heuristics such as Manhattan for the \textbf{SP} and improving on it via linear constraints penalty, and of course all the machinery necessary to fit, train and exploit some \textbf{DL}, \textbf{DRL} and \textbf{DQL} heuristics to guide search algorithms such as  A$^{*}$ and \textbf{MCTS}. Ideally I would have liked to implement things in C++ for speed and multithreading (especially for \textbf{MCTS}) but time was limited so I decided to prioritize breadth and ease of experimentation over depth and efficiency of implementation. The choice of Python definitely made it much easier to integrate with many of the ecosystem's libraries (matplotlib, pandas and pytorch in particular).

\Section{Deep Reinforcement-Q Learning}
It will not come as a surprise to anyone who has played with them that the Deep Reinforcement Learning and Deep Q Learning models can be quite capricious to train: choosing the convergence mechanisms and criteria, the interplay of generation of new training data with the inner and outer loop of the \textbf{DRL} and \textbf{DQL} algorithms (see \ref{sec:TheoryDLDRL} and \ref{sec:TheoryDQL}) seemed more of an art than a sicence at times. Obviously a lot more tuning, as well as much longer training time and computing resources would have been necessary to make these techniques more competitive at higher dimensions, but overall I remain extremely impressed by how, all things considered - and given how daunting the project seemed at first - it took me little effort to train successful \textbf{DRL} and \textbf{DQL} models capable of solving puzzles with such large state and action spaces.

\Section{Professional issues}
Bug in Kociemba and software design\\
AI safety 
See \cite{ManyWorlds}
See \cite{https://doi.org/10.1111/1758-5899.12718} and \cite{Bostrom2014}
